Supplementary Information

### 2024-07-09 supplement.Rmd
version 3 finalised

# Repeated Trust Game

Participants played a 15-round repeated trust game [@joyce_trust_1995] in the trustee role against a computer-programmed investor. Each player was represented with an icon with the participant always on the left of the screen and the opponent on the right. The participants were able to choose the icon that represents them at the start of the experiment. The icon representing the opponent changed at the start of each new game, to simulate a new interaction partner. Participants were not told they were facing computerised opponents. We chose to simulate the behavior of a human interaction partner through allowing for a delay whilst pairing with new opponents as the start of each game as well as programming the agents to respond during each round after a random time lapse (randomly chosen between 5 and 10 seconds).

```{r trustGameScreenshot, include=F, fig.cap = "Screenshot of the repeated Trust Game. The game is played in dyads, with one player assigned the role of the investor and the other player that of the trustee. The investor is endowed with 20 units at the start of each round. They need to decide how much of that endowment they want to invest with the trustee. The investment is then multiplied by a factor of 3 and sent to the trustee. The trustee in turn needs to decide how much of the multiplied investment they want to send back to the investor. Shown here is the stage at which the trustee makes a decision of how much to send back the investor", out.width="70%", out.height="70%", fig.align='center'}

@@

# Hidden markov Model used to simulate the Investor's actions

@@

## Mixed-effects models for participant returns

We fit a linear mixed effects model to participant returns as a proportion of the multiplied investment received as described below. The results of the model are presented in Table \ref{tab:myTable}

@@

mod_df <- mod_df %>%
  rownames_to_column(var = "Term") %>% 
  mutate(Term = gsub("condition.f1", "Condition", Term),
         Term = gsub("phase.f1", "Phase", Term),
         Term = gsub("high_RS1", "high_RS", Term),
         Term = gsub("inv_scaled", "Investment", Term))

# Create a summary table using apa_table
summary_table <- papaja::apa_table(
  mod_df,
  caption = "Summary of Mixed-Effects Model of participant returns over all rounds",
  align = c("l", "c", "c", "c", "c", "c")
)

@@

```{r myTable, results='asis'}
summary_table
```

@@

# References

>>>>

# A Snapshot of the Repeated Trust Game as Seen by Participants {-}

Figure \@ref(fig:trustGameScreenshot) shows a screenshot of the repeated Trust Game at the moment the participant is required to make a decision of how much to send back to the Investor.

```{r trustGameScreenshot, include=T, fig.cap = "Screenshot of the RTG as seen by participants at the decision phase.", out.width="70%", out.height="70%", fig.align='center'}

@@

# Hidden Markov Model Used to Simulate the Investor's Actions {-}

@@

# Mixed-effects Models for Participant Returns {-}

We fit a linear mixed effects model to participant returns as a proportion of the multiplied investment received as described below. The results of the model are presented in Table \@ref(tab:myTableRet)

@@

mod_df <- mod_df %>%
  rownames_to_column(var = "Term") %>% 
  mutate(Term = gsub("condition.f1", "Condition", Term),
         Term = gsub("phase.f1", "Phase", Term),
         Term = gsub("high_RS1", "RS_group", Term),
         Term = gsub("inv_scaled", "Investment", Term)) %>%
  mutate(across(where(is.numeric), ~round(., 2)))  # Round all numeric columns to 2 decimal places

@@

```{r myTableRet, results='asis'}
# Create table using kable and kableExtra
kable(mod_df, 
      caption = "Summary of Mixed-Effects Model of participant returns across all rounds",
      booktabs = TRUE,
      align = c("l", "c", "c", "c", "c", "c")) %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

# Mixed-effects Models for HMM Investments  {-}

We fit a linear mixed effects model to the investments sent by the HMM with Phase, Condition and RS groups as fixed effects, and player-wise intercepts. The results of the model are presented in Table \ref{tab:myTableInv}.

```{r, include=F}
# Create a summary object
model_inv <- readRDS("data/mod_invs_RS.RDS")

# Extract the fixed effects as a data frame
mod_df_inv <- as.data.frame(model_inv$coefficients)

mod_df_inv <- mod_df_inv %>%
  rownames_to_column(var = "Term") %>% 
  mutate(Term = gsub("condition.f1", "Condition", Term),
         Term = gsub("phase.f1", "Phase", Term),
         Term = gsub("high_RS1", "RS_group", Term)) %>%
  mutate(across(where(is.numeric), ~round(., 2)))  # Round all numeric columns to 2 decimal places

```{r myTableInv, results='asis'}
# Create table using kable and kableExtra
kable(mod_df_inv, 
      caption = "Summary of Mixed-Effects Model of HMM investments across all rounds",
      booktabs = TRUE,
      align = c("l", "c", "c", "c", "c", "c")) %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

@@

# References {-}
